Chain level Steenrod operations

### 2021-04-14 main.tex
Fix typos spotted by Federico's

We now review the group homology of finite cyclic groups. For any ring $R$ the elements
\begin{align} \label{eq: T and R definition}
T &= \rho - 1, \\
N &= 1 + \rho + \cdots + \rho^{n-1},
\end{align}
in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other. Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
\begin{equation*}
\partial(e_d) = \begin{cases}
Te_{d-1} & d \text{ odd,} \\
Ne_{d-1} & d \text{ even,}
\end{cases}
\end{equation*}
defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
\begin{equation*}
H_i(\mathrm{C}_n; \mathbb{F}_p(q)) = \mathbb{F}_p.
\end{equation*}

@@

\begin{definition} \label{def: minimal cyclic resolution}
	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
	\begin{equation*}
	\begin{tikzcd} [column sep = .5cm]
	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] \cdots
	\end{tikzcd}
	\end{equation*}
	concentrated in non-negative degrees.
\end{definition}

@@

\begin{definition} \label{def: Steenrod-Adem on surjection}
	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
	\begin{align*}
	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
	\end{align*}
	where $T$ and $R$ are defined in \eqref{eq: T and R definition}.
\end{definition}

@@

For the rest of the paper we use the McClure-Smith convention.

@@

\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.

@@

\partial (x \otimes y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &

>>>>

We now review the group homology of finite cyclic groups. For any ring $R$ the elements
\begin{equation} \label{eq: T and R definition}
\begin{split}
T &= \rho - 1, \\
N &= 1 + \rho + \cdots + \rho^{n-1},
\end{split}
\end{equation}
in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other. Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
\begin{equation*}
\partial(e_d) = \begin{cases}
Te_{d-1} & d \text{ odd,} \\
Ne_{d-1} & d \text{ even,}
\end{cases}
\end{equation*}
defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
\begin{equation*}
H_i(\mathrm{C}_p; \mathbb{F}_p(q)) = \mathbb{F}_p.
\end{equation*}

@@

\begin{definition} \label{def: minimal cyclic resolution}
	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
	\begin{equation*}
	\begin{tikzcd} [column sep = .5cm]
	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,T"'] \cdots
	\end{tikzcd}
	\end{equation*}
	concentrated in non-negative degrees.
\end{definition}

@@

\begin{definition} \label{def: Steenrod-Adem on surjection}
	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
	\begin{align*}
	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
	\end{align*}
	where $T$ and $N$ are defined in \eqref{eq: T and R definition}.
\end{definition}

@@

For the rest of the paper we use the McClure-Smith sign convention on $\mathcal X$.

@@

\partial (x \ast y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.

@@

\partial (x \ast y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
